---
title: "Final Project"
output: html_document
author: "Timothy Hanneman"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="")
#install.packages("readxl")
library(tidyverse)
library(readxl)

#library(purrr)
#library(tibble)
#library(dplyr)
#library(tidyr)
#include other packages needed here
```

```{r, eval=FALSE, include=FALSE}
#include data cleaning code here, with comments on what each step is doing the indicators above eval=FALSE and include=FALSE will stop the code from running again when you knit the document while still keeping the code in the document
#use write_csv() to write your tidy data into a new csv file

path <- "~/Documents/210Stat/FinalProject/project_tidy.csv"
things_to_try <- c("CZ Name","State","Racial Segregation","Income Segregation","Household Income per capita", "Local Tax Rate", "Local Government Expenditures Per Capita","Labor Force Participation Rate","Social Capital Index", "Fraction Religious")

Data_List <- read_excel("Manual_Cleaning.xls")
#is_tibble(Data_List)

Data_List %>% 
  select(things_to_try) %>%
  dplyr::rename_all(list(~make.names(.))) -> selected_data
write_csv(selected_data,path)
```

```{r}
#use read_csv() to import your new tidy data include any variable specifications here as needed
selected_data <- read_csv(path)
view(selected_data)
```

## Introduction
Description of data and problem(s) you are solving.  Include data source(s) here, either through citation or link to webpage.


## Graphic 1
Provide a brief description of your goal with your created graphic and what it demonstrates
```{r}
#include code for any data manipulation and variable creation used to create teh graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code

ggplot(data=selected_data, na.rm = TRUE)+
  geom_point(mapping = aes(x = Racial.Segregation, y = Local.Government.Expenditures.Per.Capita, color=State),na.rm = FALSE)
  #geom_point(mapping = aes(Local.Tax.Rate, Local.Government.Expenditures.Per.Capita,color = State))
  #coord_cartesian(xlim = c(-.1,1), ylim = c(-1, 1))
```

## Graphic 2 - if two people in group
Provide a brief description of your goal with your created graphic and what it demonstrates
```{r}
#include code for any data manipulation and variable creation used to create teh graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
ggplot(data=selected_data, na.rm = TRUE)+
  geom_point(mapping = aes(Local.Tax.Rate, Local.Government.Expenditures.Per.Capita,color = State))
```


## Graphic 3 - if three people in group
Provide a brief description of your goal with your created graphic and what it demonstrates
```{r}
#include code for any data manipulation and variable creation used to create teh graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
ggplot(data=selected_data, na.rm = TRUE)+
  geom_point(mapping = aes(Social.Capital.Index, Local.Government.Expenditures.Per.Capita,color = State))
```