---
title: "Final Project"
output: html_document
author: "Timothy Hanneman"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="")
#install.packages("readxl")
library(tidyverse)
library(readxl)

#library(purrr)
#library(tibble)
#library(dplyr)
#library(tidyr)
#include other packages needed here
```

```{r, eval=FALSE, include=FALSE}
#include data cleaning code here, with comments on what each step is doing the indicators above eval=FALSE and include=FALSE will stop the code from running again when you knit the document while still keeping the code in the document
#use write_csv() to write your tidy data into a new csv file

#This is where I am storing the files
path <- "~/Documents/210Stat/Stat_210_Final_Project/project_tidy.csv"
#This is what it's going to selected out of the original data
things_to_try <- c("CZ Name","State","Racial Segregation","Income Segregation","Household Income per capita", "Local Tax Rate", "Local Government Expenditures Per Capita","Labor Force Participation Rate","Social Capital Index", "Fraction Religious")

#Lets load the excel file
Data_List <- read_excel("Manual_Cleaning.xls")
#is_tibble(Data_List)

#Lets clean it up
Data_List %>% 
  select(things_to_try) %>%
  #This line of code fixes the titles to make them easier to select in R
  dplyr::rename_all(list(~make.names(.))) -> selected_data
#Making the new csv file
write_csv(selected_data,path)
```

```{r}
#use read_csv() to import your new tidy data include any variable specifications here as needed
#It won't knit without the path variable being placed here as well...
path <- "~/Documents/210Stat/Stat_210_Final_Project/project_tidy.csv"
selected_data <- read_csv(path)
#view(selected_data)
```

## Introduction
Description of data and problem(s) you are solving.  Include data source(s) here, either through citation or link to webpage.

The original data set came from a scientific investigation of social mobility among children. It measured a large number of characteristics of neighborhoods and differences in outcomes using children who changed neighborhoods as a control. I thought it would be interesting to plot some of the data as a simple investigation of how different factors might related to each other. The project can be found at https://opportunityinsights.org/data/. The dataset is named "Where is the Land of Opportunity? The Geography of Intergenerational Mobility in the United States." I learned about the dataset from http://freakonomics.com/podcast/american-dream-really-dead/ . It also includes an online lecture that has been used at Stanford & Harvard for using stats & data for economic and social problems.



## Graphic 1
The goal is data exploration.

Does the plot of racial segregation show any relation into local government expenditures per capita?
The graph is of multiple localities within each of the 50 states.
For further investigation it would be interesting to see if the various states could be grouped into larger geographical gropus to see if there are any differences by region. I wouldn't make any conclusions based just on these graphs without trying to control for other factors.

```{r}
#Lets try plotting two variables in the prepared data.
ggplot(data=selected_data, na.rm = TRUE)+
  geom_point(mapping = aes(x = Racial.Segregation, y = Local.Government.Expenditures.Per.Capita, color=State),na.rm = FALSE)

```

## Graphic 2 - (Extra investigation)
Lets examine something that seems more likely to be related, expenditures and tax rate. Let look at a few of the places in California
since this is where we are at.

```{r}
#Use the preselected data
selected_data %>%
  #Choose only California data points
  filter(State == "CA") %>%
  #Use a simple graph
  ggplot(na.rm = TRUE)+
    geom_point(mapping = aes(Local.Tax.Rate, Local.Government.Expenditures.Per.Capita,color = State))
```


## Graphic 3 - (Extra investigation)
Lets take a look at social capital defined by google as "the networks of relationships among people who live and work in a particular society, enabling that society to function effectively.". Is there any relationship between Social Capital and Government expenditures?

```{r}
# Use the prepared data
selected_data %>%
  #We want to look at California data
  filter(State == "CA") %>%
  #Lets plot it
  ggplot(na.rm = TRUE)+
    geom_point(mapping = aes(Social.Capital.Index, Local.Government.Expenditures.Per.Capita,color = State))
```